### 2020-02-12 writeup/setup.tex
wip

\section{Problem setup: The multi-task learning problem}\label{sec_setup}

%    \item {\bf The distributed learning problem.}
%    \begin{align}
 %     f(w) = \sum_{i=1}^k \normFro{X_i w - Y_i}^2. \label{eq_dist}
 %   \end{align}
 %   A natural setting is when the covariance matrices $X_i^{\top} X_i$ are different, i.e. having different spetrum.
 %   This is also known as covariate shift in the literature.
 %   Our hypothesis is that the covariate shift can slow down the convergence of learning the true $\theta$ as a function of the number of data opints.

    \paragraph{Different covariates:}
    If we follow the model setup of the first problem, but consider the following objective instead.
    \begin{align}
        f(B; A_1, \dots, A_k) = \sum_{i=1}^k \normFro{X_i B A_i - Y_i}^2.
    \end{align}
    This is a slightly more complicated parameterization of the first problem, in that each $A_i$ can select a model from the subspace of $B$ to fit $(X_i, Y_i)$.

    \paragraph{Different models:} The most general version is when the covariates are different between different tasks and the single-task models are also different.
    Here the hypothesis is that the optimal $B$ is captured by a low-rank approximation of the single-task models.

\section{General hypothesis}

@@

\subsection{Covariate shift}

@@

Since the models are same, the most natural objective is using Equation \eqref{eq_dist}.

\begin{proposition}
  Show that adding tasks always helps or reduces estimation error.
\end{proposition}

\paragraph{The case of two tasks: $k = 2$.} We would like to get insight on how the covariate shift results in slower rates of transfer. The key quantity is to look at:
\begin{align}
  \tr[(X_1^{\top}X_1 + X_2^{\top} X_2)^{-1}]
\end{align}

\subsection{Model shift}

>>>>

\section{Problem Setup}\label{sec_setup}

In the multi-task learning (MTL) problem, we are given the input of $k$ tasks $(X_1, Y_1), (X_2, Y_2), \dots, (X_k, Y_k)$.
We use a shared module $B$ for all tasks and a separate module $\set{A_i}_{i=1}^k$ for each task.
%    \paragraph{Different covariates:}
This corresponds to minimizing the following optimization objective.
\begin{align}
	\label{eq_mtl}
	f(B; A_1, \dots, A_k) = \sum_{i=1}^k \normFro{X_i B A_i - Y_i}^2.
\end{align}

When the models are the same for all tasks, we use a simplified objective as follows.
\begin{align}
	\label{eq_mtl_basic}
	f(w) = \sum_{i=1}^k \normFro{X_i w - Y_i}^2.
\end{align}
%{\bf The distributed learning problem.}
%    \begin{align}
%     f(w) = \sum_{i=1}^k \normFro{X_i w - Y_i}^2. \label{eq_dist}
%   \end{align}

Equation \eqref{eq_mtl} is a slightly more complicated parametrization of equation \eqref{eq_mtl_basic}, in that each $A_i$ can select a model from the subspace of $B$ to fit $(X_i, Y_i)$.

\subsection{Hypothesis}

@@

\subsubsection{Covariate Shift}

A natural setting is when the covariance matrices $X_i^{\top} X_i$ are different, i.e. having different spectrum.
This is also known as covariate shift in the literature.
Our hypothesis is that the covariate shift can slow down the convergence of learning the true $\theta$ as a function of the number of data opints.

@@

\subsubsection{Model Shift}

The most general version is when the covariates are different between different tasks and the single-task models are also different.
Here the hypothesis is that the optimal $B$ is captured by a low-rank approximation of the single-task models.
